### 2020-03-04 doc/icfp20/harmony.tex
restore some code

\newcommand{\Harmonization}{
  \begin{figure}
    \includegraphics[width=5.5cm]{fig/piston.png}
    \hspace{1cm}
    \includegraphics[width=5cm]{fig/fharm.png} \\
    \begin{flushleft}
    \begin{small}
     \hspace{2.35cm} V \ \ \ \ \ \ \ \,I \ \ \ \ \ \ \ \,IV \,VI \ \,III \ IV \ \ \,V
     \hspace{2.6cm} V \ \ \ \ \ \ \ \,I \ \ \ \ \ \,IV VI \,III\,IV \ \ V
    \end{small}
    \end{flushleft}
    \caption{Harmonization by Piston (left) and \fharm (right)}
    \Description{Harmonization by Piston (left) and \fharm (right)}
    \label{fig:harmonization}
  \end{figure}
}

\newcommand{\HarmonizationMT}{
  \begin{figure}
    \includegraphics[width=5.5cm]{fig/piston.png}
    \hspace{1cm}
    \includegraphics[width=5cm]{fig/fharm.png} \\
    \begin{flushleft}
    \begin{small}
     \hspace{2.35cm} V \ \ \ \ \ \ \ \,I \ \ \ \ \ \ \ \,IV \,VI \ \,III \ IV \ \ \,V
     \hspace{2.6cm} V \ \ \ \ \ \ \ \,I \ \ \ \ \ \,IV VI \,III\,IV \ \ V
    \end{small}
    \end{flushleft}
    \caption{Harmonization by Music Tools (to be replaced by real figure)}
    \Description{Harmonization by Music Tools}
    \label{fig:harmonizationMT}
  \end{figure}
}

@@

rootProgression : Triad \(\rightarrow\) NextTriad
rootProgression I   = nextTriad (IV :: V :: []) (VI :: []) (II :: III :: [])
rootProgression II  = nextTriad (V :: []) (IV  :: VI :: []) (I :: III :: [])
-- other cases omitted for space
\end{alltt}

@@

\begin{alltt}
previousTriads : Triad \(\rightarrow\) List Triad
previousTriads I   = V :: IV :: VII :: []
previousTriads II  = VI :: IV :: []
-- other cases omitted for space
\end{alltt}

>>>>

\newcommand{\Harmonization}{
  \begin{figure}
    \includegraphics[width=5.5cm]{fig/piston.png}
    \hspace{1cm}
    \includegraphics[width=5cm]{fig/fharm.png} \\
    \begin{flushleft}
    \begin{small}
     \hspace{2.35cm} V \ \ \ \ \ \ \ \,I \ \ \ \ \ \ \ \,IV \,VI \ \,III \ IV \ \ \,V
     \hspace{2.6cm} V \,III \ \ I \ III \ \,II IV \,III\,IV \ \,V
    \end{small}
    \end{flushleft}
    \caption{Harmonization by Piston (left) and \fharm (right)}
    \Description{Harmonization by Piston (left) and \fharm (right)}
    \label{fig:harmonization}
  \end{figure}
}

\newcommand{\HarmonizationMT}{
  \begin{figure}
    \includegraphics[width=5.5cm]{fig/harmmt.png}
    \begin{flushleft}
    \begin{small}
     \hspace{5.4cm} I \ \ V \ \ \ VI \ \,V \ \ IV \ I \ \ \ V  \,IV \ \ \ \ V
    \end{small}
    \end{flushleft}
    \caption{Harmonization by Music Tools}
    \Description{Harmonization by Music Tools}
    \label{fig:harmonizationMT}
  \end{figure}
}

@@

rootProgression : Triad \(\rightarrow\) NextTriad
rootProgression I   = nextTriad (IV :: V :: []) (VI :: []) (II  :: III : [])
rootProgression II  = nextTriad (V :: []) (IV :: VI :: []) (I :: III :: [])
rootProgression III = nextTriad (VI :: []) (IV :: []) (I :: II :: V :: [])
rootProgression IV  = nextTriad (V :: []) (I :: II :: []) (III :: VI :: [])
rootProgression V   = nextTriad (I :: []) (IV :: VI :: []) (II :: III :: [])
rootProgression VI  = nextTriad (II :: V :: []) (III :: IV :: []) (I :: [])
rootProgression VII = nextTriad (I  :: III :: []) (VI :: []) (II :: IV  :: V :: [])
\end{alltt}

@@

\begin{alltt}
previousTriads : Triad \(\rightarrow\) List Triad
previousTriads I   = V :: IV :: VII :: []
previousTriads II  = VI :: IV :: []
previousTriads III = VI :: VII :: []
previousTriads IV  = I :: V :: II :: III :: []
previousTriads V   = I :: IV :: II :: VI :: []
previousTriads VI  = IV :: I :: II :: V :: VII :: []
previousTriads VII = []
\end{alltt}
